---
title: 'Example project'
subtitle: ''
author: ''
date: 'Last update: `r Sys.time()`'
output: html_document
bibliography: r-references.bib
---


```{r, echo=F, warning=F, message=F}
library(knitr)
library(tidyverse)
library(here)
library(broom)
```

## Chunks

- `echo`: logical (TRUE/FALSE)
- `eval`: logical (TRUE/FALSE)
- `include`: logical (TRUE/FALSE)

```{r, 'load-data', echo=T, message=F}
dat <- read_csv(here("data", "simulated_data.csv"))
```

## Plots

Important chunk options

- `fig.retina`: numeric (1 or 2)
- `fig.width`: numeric
- `fig.height`: numeric
- `fig.align`: character ('left', 'right', 'center')

```{r, scatter-plot}
dat %>% 
  ggplot() + 
  aes(x = days, y = score) + 
    geom_point()
```



## Tables

Important chunk options

- `results`: character ('hide', 'asis')

### Descriptive stats

```{r, desc-tab, results='asis'}
dat %>% 
  summarize(n = n(), avg_score = mean(score), sd_score = sd(score)) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  kable(format = "pandoc")
```




### Fit a model

```{r, model}
# Score as a function of days without sleep
mod <- lm(score ~ days, data = dat)

# Model summary
summary(mod)

# Assign to tidy object for cleaner printing
mod_tib <- tidy(mod) %>% 
  mutate_if(is.numeric, round, digits = 2)
```


```{r, mod-tab1}
mod_tib %>% 
  kable(format = "pandoc")
```


```{r, mod-tab2, message=F, eval=F}
sjPlot::tab_model(mod)
```







## Writing results

We analyzed the simulated data using linear regression. 
The outcome variable, `score` was modeled as a function of days without sleep. 
The model estimate for the intercept was `r mod_tib[1, 2]` &pm;`r mod_tib[1, 3]` standard errors (*t* = `r mod_tib[1, 4]`, p < .001). 
Scores decreased as days without sleep increased. 
Specifically, for each day without sleep scores decreased by `r mod_tib[2, 2]` &pm; `r mod_tib[2, 3]` standard errors (*t* = `r mod_tib[2, 4]`, p < .001). 







## Different outputs

We can change the `output: ` argument of the YAML front matter. 
Try `output: word_document` and `output: pdf_document` (if you have LaTeX installed). 
We can also change the style of the documents using CSS (see output options). 







## Ref sections

You can use `.bib` files to automate reference sections. 

Add this to the YAML front matter: 

```
bib: r-references.bib
```

And then cite anything in the r-references.bib file using \@ and the ref name. 
For example, we did our analysis in R [@R-base]. 
References don't have to be parenthetical.  
@R-papaja was used for APA formatting. 

For more information about APA formatting with `papaja`, see the `example_apa.Rmd` file. 



# References
